Project-I by Group Sao Paulo

### 2015-11-02 report/paper.tex
Refactored part of the first sections
Update report and figures

\begin{abstract}
In this report, we 
\end{abstract}

\section{Regression}
\subsection{Data Description}
Our regression-data contains $N=2800$ train-examples and $N=1200$ test-data. The train-data are composed of input and output variables $X$ and $y$. Each input $x_n$ has a dimensionality $D=70$ with 60 real-valued variables, 1 binary variable, 5 and 4 categorical variables with respectively 3 and 4 categories. The output of our test-data is not observed. Our goal is then to predict $y$ for all test-examples and to give an approximation of the test-error.

@@

>>>>

\begin{abstract}
In this report, we study several linear method to compute regression and classification on two different datasets. For the regression part, we used k-means clustering to separate the data in three clusters. As the input matrix is ill-conditioned, we applied a PCA algorithm to reduce its dimensionality. WHICH ALGORITHM IS THE BEST; IDEA OF ERROR. For the classification part, we separate the data given their distribution along the dimensions of the input. WHICH ALGORITHM IS THE BEST; IDEA OF ERROR.
\end{abstract}

\section{Regression}
\subsection{Data Description}
Our regression-data contains $N=2800$ train-examples and $N=1200$ test-data. The
train-examples are composed of input and output variables $X$ and $y$. Each
input $x_n$ has a dimensionality $D=70$ with 60 real-valued variables, 1 binary
variable, 5 and 4 categorical variables with respectively 3 and 4 categories.
The output of our test-data is not observed. Our goal is then to predict $y$ for
all test-examples and to give an approximation of the test-error.

@@

Figure TODO shows the train and test TODO ERROR for $\lambda$ varied from
